---
title: "Discretize"
author: "EVaR"
date: "2022-11-16"
output: 
  pdf_document:
    extra_dependencies: [amsmath,bbm]
---

```{r}
setwd("C:/GITHUB/Rasr_submit")
source("Code/RASR_code.R")
```

# Entropic Risk Measure
We define ERM for $beta > 0$ as:
\[
\text{ERM}_\beta[X] = -\beta^{-1}{\log(\mathbb{E}[e^{-\beta X}])}
\]
, $\text{ERM}_{0}[X] = \mathbb{E}[X]$ and $\text{ERM}_{1}[X] = \min[X]$. Furthermore, it can be written as 
\[
\text{ERM}_\beta[X] = \inf_Z\{ \mathbb{E}[ZX] - \frac{\mathbb{E}[Z\log(Z)]}{\beta}: \mathbb{E}[Z \cdot e^{-\beta X}] \leq 1\}
\]
\[
\text{ERM}_\beta[X] = \inf_\alpha\{ \text{EVaR}_\alpha[X] - \frac{\log(\alpha)}{\beta}\}
\]
ERM has utility function
\[
U_\text{ERM}^\beta(x) = \frac{1-e^{-\beta x}}{\beta}
\]

# Entropic Value at Risk

Here we define EVaR as 
\[
\text{EVaR}_\alpha[X] = \max_\beta\{\text{ERM}_\beta[X] + \log(\alpha) \} 
\]
EVaR has utility function
\[
U_\text{EVaR}^\alpha(x) = x \cdot \frac{e^{-\beta^\star x}}{\mathbb{E}[e^{-\beta^\star X}]}
\]
where $\beta^\star = \text{argmax}_\beta\{ -\beta^{-1} \cdot [\log(\mathbb{E}[e^{-\beta X}])-\log(\alpha)] \}$. Furthermore, let $Z^\star = \frac{e^{-\beta^\star X}}{\mathbb{E}[e^{-\beta^\star X}]}$ we have $\mathbb{E}[Z^\star] = 1$ and $\mathbb{E}[Z^\star \log(Z^\star)] = -\log(\alpha)$. Property (P1) follows from the dual of EVaR:
\[
\mathbb{E}[U_\text{EVaR}^\alpha(x)] = \mathbb{E}[X \cdot \frac{ e^{-\beta^\star X}}{\mathbb{E}[e^{-\beta^\star X}]}] = 
\mathbb{E}[X \cdot Z^\star]
=\inf_{Z > 0}\{\mathbb{E}[XZ] : \mathbb{E}[Z]=1,\mathbb{E}[Z\log(Z)]\leq -\log(\alpha)\}
\]

The conditional EVaR can be formulate as 
\[
\text{EVaR}_\alpha[X] =\inf_Z\{ \mathbb{E}[Z \cdot \text{EVaR}_{\alpha \cdot \exp(-\mathbb{E}[Z \log(Z)])}[X|S']]\}
\]
Proof:
\[
\text{EVaR}_\alpha[X] = \sup_\beta\{ \text{ERM}_\beta[X] +\frac{\log(\alpha)}{\beta} \} =  \text{ERM}_{\beta^\star}[X] +\frac{\log(\alpha)}{\beta^\star}
\]
\[
= \text{ERM}_{\beta^\star}[\text{ERM}_{\beta^\star}[X|S']] +\frac{\log(\alpha)}{\beta^\star}
\]
\[
= \text{ERM}_{\beta^\star}[\inf_{\alpha'}\{ \text{EVaR}_{\alpha'}[X|S'] - \frac{\log({\alpha'})}{\beta}\}] +\frac{\log(\alpha)}{\beta^\star}
\]
\[
= \text{ERM}_{\beta^\star}[\inf_{Z_{S'}}\{ \text{EVaR}_{\alpha Z_{S'}}[X|S'] - \frac{\log({\alpha Z_{S'}})}{\beta ^\star}\}] +\frac{\log(\alpha)}{\beta^\star}
\]
\[
= \text{ERM}_{\beta^\star}[\inf_{Z_{S'}}\{ \text{EVaR}_{\alpha Z_{S'}}[X|S'] - \frac{\log({\alpha Z_{S'}})}{\beta ^\star}\}] +\frac{\log(\alpha)}{\beta^\star}
\]
\[
\inf_Z\{ \mathbb{E}[Z \cdot\inf_{Z_{S'}}\{ \text{EVaR}_{\alpha Z_{S'}}[X|S'] - \frac{\log({\alpha Z_{S'}})}{\beta ^\star}\}] - \frac{\mathbb{E}[Z\log(Z)]}{\beta ^\star}: \mathbb{E}[Z \cdot e^{-\beta^\star X}] \leq 1\}
+\frac{\log(\alpha)}{\beta^\star}
\]
\[
\inf_Z\{ \inf_{Z_{S'}}\{\mathbb{E}[Z \cdot \text{EVaR}_{\alpha Z_{S'}}[X|S']] +\frac{-\log({\alpha Z_{S'}})+\log(\alpha)-\mathbb{E}[Z\log(Z)]}{\beta^\star}: \mathbb{E}[Z \cdot e^{-\beta^\star X}] \leq 1\}\}
\]
If $-\log({\alpha Z_{S'}})+\log(\alpha)-\mathbb{E}[Z\log(Z)] = 0$ implies $Z_{S'} = e^{-\mathbb{E}[Z \log(Z)]}$
\[
=\inf_Z\{ \mathbb{E}[Z \cdot \text{EVaR}_{\alpha \cdot \exp(-\mathbb{E}[Z \log(Z)])}[X|S']]\}
\]
\[
\neq\inf_Z\{ \mathbb{E}[Z \cdot \text{EVaR}_{\alpha \cdot Z}[X|S']]\}
\]
# Example



```{r}
X1 = data.frame(x = c(1,10),p = c(0.2,0.8))
X2 = data.frame(x = c(2,10),p = c(0.9,0.1))
condp = c(0.3,0.7)

Xjoint = data.frame(x = c(1,2,10),p =c(0.06,0.63,0.31))

beta = 0.5
logZ = -beta*(Xjoint$x - ERM(Xjoint$x,alpha=beta,prob=Xjoint$p))
Z = exp(logZ)
Eebx = exp(-beta*ERM(Xjoint$x,alpha=beta,prob=Xjoint$p))
alpha = exp(-E(X=exp(logZ)*logZ,prob=Xjoint$p))
soln = sum(Z*Xjoint$x*Xjoint$p)
soln
```


```{r}
logZ1 = -beta*(X1$x - ERM(X1$x,alpha=beta,prob=X1$p))
logZ2 = -beta*(X2$x - ERM(X2$x,alpha=beta,prob=X2$p))
Z1 = exp(logZ1)
Z2 = exp(logZ2)
Eebx1 = exp(-beta*ERM(X1$x,alpha=beta,prob=X1$p))
Eebx2 = exp(-beta*ERM(X2$x,alpha=beta,prob=X2$p))
Eebxnew = exp(-beta*ERM(c(ERM(X1$x,alpha=beta,prob=X1$p),ERM(X2$x,alpha=beta,prob=X2$p)),
                        alpha=beta,
                        prob=condp))
alpha1 = exp(-E(X=exp(logZ1)*logZ1,prob=X1$p))
alpha2 = exp(-E(X=exp(logZ2)*logZ2,prob=X2$p))
zt1 = alpha1/alpha
zt2 = alpha2/alpha
# The wrong solution can be computed as
cat("wrong method",E(X = c(zt1 * E(Z1*X1$x,prob=X1$p),zt2 * E(Z2*X2$x,prob=X2$p)),prob = condp))
# The right solution can be computed as 
library(lamW)
mixz1 = Eebx1/Eebx
mixz2 = Eebx2/Eebx
cat("\nmaybe right method",E(X = c(mixz1 * E(Z1*X1$x,prob=X1$p),mixz2 * E(Z2*X2$x,prob=X2$p)),prob = condp))
```

